$\XX$ dubious ways of estimating $\rr$

### 2018-07-03 paper/draft_v8/draft_v8.tex
finally on git

We then generate random errors that are added to the X and Y compartments at each time step in order to simulate some form of randomness. \textbf{The sum of these was then subtracted from the Z compartment in order to keep the total population in the system constant.} We generated data sets with two different types of errors: Gaussian and autoregressive. \textbf{The Gaussian errors are independently distributed with mean 0 and constant variance for the entire length of the time series. The autoregressive errors are generated from a first-order process of the form: $$ \epsilon_{t} = \rho * \epsilon_{t-1} + \delta_{t}$$, where $\rho$ is fixed throughout and $\delta_{t} \sim N(0, \sigma)$ with constant $\sigma$. The values of the variances are chosen somewhat arbitrarily, although they are intended to be fairly small at first.}

@@

Below, we compare the estimates and standard errors of $\rr$ given by each of the models for a few selected data sets. The forest plots below show the point estimates and 95\% confidence intervals of $\rr$ from each model for a particular data set. The true $\rr$ value is also shown by the vertical red line in the graphs.

All of the figures below show results from data sets that were simulated with added Gaussian errors. The plot on the top left shows the estimates from one of the baseline data sets. For the most part, the $\rr$ values range from approximately 0.8 to 1.4. We note that the range of values includes $\rr$ values of less than 1, meaning that some models predict that a disease is not spreading when it actually is. However, on the whole, the variation of estimates between models is smaller than we originally expected. The confidence intervals are very small relative to the estimates for the most part; exceptions to this include the SIR IPR and the Markov chain model as the exception.

The plot on the top right shows the estimates for the data set where $Y_0$ is increased to 100. The $\rr$ estimates generally seem to be further away from the true $\rr$ value compared to the results from the baseline data sets, and the overall . The confidence intervals are also more often than not larger than those in the baseline. In particular, the standard errors for some of the SIR models increase by several orders of magnitude.

The bottom left plot shows the estimates for the data set where the error added to the generated data is increased. For most of the models, the estimates of $\rr$ do not change very much compared to the baseline data set. The confidence intervals for this data set increase for some of the models, such as the SIR LMA, while they remain approximately the same as the baseline data sets for most of the others.

On the bottom right, we see the $\rr$ estimates for the case when disease prevalence grows linearly, as opposed to exponentially as seen in the data sets generated under SIR conditions, where the disease prevalence grows exponentially. Model performance here varies depending on how well the models the aforementioned linear growth. Some of the models, such as the SIR Markov chain and the IPR models, do not handle this case very well, giving much larger estimates and standard errors than are reasonable. On the other hand, models such as the SIR maximum and final size seem to be more flexible to different trajectories. [The error bars do not show up if they go outside of the x-axis limits - how do we fix this?]

\begin{minipage}{0.5\linewidth}
	\includegraphics[width=3in]{BaselineFP.jpeg}
\end{minipage}
\begin{minipage}{0.5\linewidth}
	\includegraphics[width=3in]{StartPopFP.jpeg}
\end{minipage}

\begin{minipage}{0.5\linewidth}
	\includegraphics[width=3in]{VarianceFP.jpeg}
\end{minipage}
\begin{minipage}{0.5\linewidth}
	\includegraphics[width=3in]{OtherFP.jpeg}
\end{minipage}

@@

\begin{table}[H]
	\caption{$\rr$ Estimates and Std. Errs, SIR Model, 
		Baseline Data, $X_0 = 99950, Y_0 = 50$, 
		$\sigma_X = 10, \sigma_Y = 1$}
	\begin{footnotesize}
		\hskip -1cm
		\begin{tabular}{l|r|r|r|r|r|r|r|r}
			\hline
			Data Set & Auto Est & Auto SE & AutoM Est & AutoM SE & Norm Est & Norm SE & NormM Est & NormM SE\\
			\hline
			Baseline 1 & 1.965322 & 0.000869 & 1.983308 & 0.000882 & 2.005867 & 0.000893 & 1.994736 & 0.000884\\
			\hline
			Baseline 2 & 2.039608 & 0.000913 & 1.999245 & 0.000895 & 2.001217 & 0.000889 & 1.995960 & 0.000887\\
			\hline
			Baseline 3 & 2.005609 & 0.000901 & 1.966631 & 0.000873 & 2.016216 & 0.000901 & 1.997175 & 0.000887\\
			\hline
			Baseline 4 & 1.958037 & 0.000859 & 1.941109 & 0.000852 & 1.995544 & 0.000886 & 2.004107 & 0.000892\\
			\hline
			Baseline 5 & 2.050904 & 0.000926 & 1.964328 & 0.000866 & 2.009912 & 0.000896 & 1.990153 & 0.000881\\
			\hline
		\end{tabular}
	\end{footnotesize}
\end{table}

@@

	\caption{$\rr$ Estimates and Std. Errs, SIR Model,
		Different Starting Populations, 
		$\sigma_X = 10, \sigma_Y = 1$}
	\begin{footnotesize}
		\hskip -1.7cm
		\begin{tabular}{l|r|r|r|r|r|r|r|r}
			\hline
			Data Set & Auto Est & Auto SE & AutoM Est & AutoM SE & Norm Est & Norm SE & NormM Est & NormM SE\\
			\hline
			$X_0 = 99999, Y_0 = 1$ & 1.689292 & 0.020794 & -4.167216 & 0.168853 & 1.976254 & 0.045081 & 1.688593 & 0.029680\\
			\hline
			$X_0 = 99990, Y_0 = 10$ & 2.038297 & 0.004597 & 2.207003 & 0.005165 & 2.037726 & 0.004596 & 1.883084 & 0.004049\\
			\hline
			$X_0 = 99900, Y_0 = 100$ & 2.009581 & 0.000449 & 2.006557 & 0.000448 & 1.999236 & 0.000445 & 1.995467 & 0.000444\\
			\hline
			$X_0 = 99000, Y_0 = 1000$ & 2.002521 & 0.000046 & 2.001829 & 0.000046 & 1.999519 & 0.000046 & 2.000098 & 0.000046\\
			\hline
		\end{tabular}
	\end{footnotesize}
\end{table}

@@

	\caption{$\rr$ Estimates and Std. Errs, SIR Model, 
		Different Variances, $X_0 = 99000$, $Y_0 = 1000$}
	\begin{footnotesize}
		\hskip -1.7cm
		\begin{tabular}{l|r|r|r|r|r|r|r|r}
			\hline
			Data Set & Auto Est & Auto SE & AutoM Est & AutoM SE & Norm Est & Norm SE & NormM Est & NormM SE\\
			\hline
			$\sigma_X = 10, \sigma_Y = 1$ & 1.927444 & 0.000059 & 1.927090 & 5.9e-05 & 1.925768 & 5.9e-05 & 1.926576 & 5.9e-05\\
			\hline
			$\sigma_X = 100, \sigma_Y = 10$ & 1.926786 & 0.000058 & 1.916571 & 5.9e-05 & 1.919778 & 5.9e-05 & 1.929422 & 5.9e-05\\
			\hline
			$\sigma_X = 300, \sigma_Y = 30$ & 1.994211 & 0.000062 & 1.976893 & 5.8e-05 & 1.930660 & 5.8e-05 & 1.920869 & 5.9e-05\\
			\hline
			$\sigma_X = 1000, \sigma_Y = 100$ & 1.749057 & 0.000050 & 1.736588 & 5.9e-05 & 2.003654 & 6.2e-05 & 1.897049 & 5.9e-05\\
			\hline
			$\sigma_X = 3000, \sigma_Y = 300$ & 1.992674 & 0.000063 & 1.681585 & 4.9e-05 & 1.959815 & 6.7e-05 & 1.770816 & 5.3e-05\\
			\hline
			$\sigma_X = 10000, \sigma_Y = 1000$ & -42.264180 & 0.002694 & 1.773388 & 3.1e-05 & 1.889188 & 6.6e-05 & 2.649010 & 6.3e-05\\
			\hline
		\end{tabular}
	\end{footnotesize}
\end{table}

@@

	\caption{$\rr$ Estimates and Std. Errs, SIR Model,
		Other Models, $X_0 = 99950, Y_0 = 50$, 
		$\sigma_X = 10, \sigma_Y = 1$}
	\begin{footnotesize}
		\hskip -1cm
		\begin{tabular}{l|r|r|r|r|r|r|r|r}
			\hline
			Data Set & Auto Est & Auto SE & AutoM Est & AutoM SE & Norm Est & Norm SE & NormM Est & NormM SE\\
			\hline
			0th & -2.032207 & 0.244058 & 1.229963 & 0.069020 & 1.021369 & 0.056558 & 0.795460 & 0.331468\\
			\hline
			1st & 1.038117 & 0.000029 & 1.037889 & 0.000029 & 1.037902 & 0.000029 & 1.037887 & 0.000029\\
			\hline
			2nd & 1.198856 & 0.000045 & 1.198589 & 0.000045 & 1.198772 & 0.000045 & 1.198501 & 0.000045\\
			\hline
			3rd & 1.202405 & 0.000043 & 1.202098 & 0.000043 & 1.202350 & 0.000043 & 1.202240 & 0.000043\\
			\hline
			4th & 1.210597 & 0.000047 & 1.210597 & 0.000047 & 1.210194 & 0.000047 & 1.210304 & 0.000047\\
			\hline
			Linear SIR & 1.274346 & 0.000034 & 1.273739 & 0.000034 & 1.274229 & 0.000034 & 1.273950 & 0.000034\\
			\hline
		\end{tabular}
	\end{footnotesize}
\end{table}

@@

	\caption{$\rr$ Estimates and Std. Errs, SIRREPAR Model,
		Baseline Data, $X_0 = 99950, Y_0 = 50$, 
		$\sigma_X = 10, \sigma_Y = 1$}
	\begin{footnotesize}
		\hskip -1cm
		\begin{tabular}{l|r|r|r|r|r|r|r|r}
			\hline
			Data Set & Auto Est & Auto SE & AutoM Est & AutoM SE & Norm Est & Norm SE & NormM Est & NormM SE\\
			\hline
			Baseline 1 & 3.226272 & 0.000000 & 1.984447 & 0.000294 & 2.006310 & 0.000298 & 1.993558 & 0.000294\\
			\hline
			Baseline 2 & 3.203012 & 0.000000 & 1.999589 & 0.000299 & 2.000868 & 0.000297 & 1.995630 & 0.000296\\
			\hline
			Baseline 3 & 4.180804 & 0.000733 & 4.180810 & 0.000724 & 5.043355 & 0.000908 & 1.997399 & 0.000296\\
			\hline
			Baseline 4 & 4.180819 & 0.000709 & 4.180816 & 0.000715 & 1.995237 & 0.000295 & 2.003821 & 0.000298\\
			\hline
			Baseline 5 & 4.180799 & 0.000741 & 4.180815 & 0.000717 & 2.008713 & 0.000300 & 4.180812 & 0.000720\\
			\hline
		\end{tabular}
	\end{footnotesize}
\end{table}

@@

	\caption{$\rr$ Estimates and Std. Errs, SIRREPAR Model,
		Different Starting Populations, 
		$\sigma_X = 10, \sigma_Y = 1$}
	\begin{footnotesize}
		\hskip -1.7cm
		\begin{tabular}{l|r|r|r|r|r|r|r|r}
			\hline
			Data Set & Auto Est & Auto SE & AutoM Est & AutoM SE & Norm Est & Norm SE & NormM Est & NormM SE\\
			\hline
			$X_0 = 99999, Y_0 = 1$ & 5.899238 & 0.025009 & 5.898924 & 0.051433 & 3.394166 & 0.000021 & 3.217232 & 0.000016\\
			\hline
			$X_0 = 99990, Y_0 = 10$ & 3.162364 & 0.000001 & 3.170152 & 0.000002 & 3.131576 & 0.000001 & 3.108194 & 0.000001\\
			\hline
			$X_0 = 99900, Y_0 = 100$ & 4.564960 & 0.000404 & 2.005939 & 0.000150 & 1.998880 & 0.000149 & 1.994592 & 0.000148\\
			\hline
			$X_0 = 99000, Y_0 = 1000$ & 47.241714 & 0.002493 & 47.241714 & 0.002511 & 47.241714 & 0.002502 & 47.241714 & 0.002502\\
			\hline
		\end{tabular}
	\end{footnotesize}
\end{table}

@@

	\caption{$\rr$ Estimates and Std. Errs, SIRREPAR Model,
		Different Variances, 
		$X_0 = 99000, Y_0 = 1000$}
	\begin{footnotesize}
		\hskip -1.7cm
		\begin{tabular}{l|r|r|r|r|r|r|r|r}
			\hline
			Data Set & Auto Est & Auto SE & AutoM Est & AutoM SE & Norm Est & Norm SE & NormM Est & NormM SE\\
			\hline
			$\sigma_X = 10, \sigma_Y = 1$ & 1.926733 & 4e-06 & 1.927468 & 4e-06 & 1.925555 & 4e-06 & 1.926689 & 4e-06\\
			\hline
			$\sigma_X = 100, \sigma_Y = 10$ & 1.925550 & 4e-06 & 1.916380 & 4e-06 & 1.920075 & 4e-06 & 1.928987 & 4e-06\\
			\hline
			$\sigma_X = 300, \sigma_Y = 30$ & 1.994719 & 4e-06 & 1.976273 & 4e-06 & 1.930978 & 4e-06 & 1.920290 & 4e-06\\
			\hline
			$\sigma_X = 1000, \sigma_Y = 100$ & 1.749031 & 3e-06 & 1.736589 & 3e-06 & 2.003044 & 4e-06 & 1.897328 & 4e-06\\
			\hline
			$\sigma_X = 3000, \sigma_Y = 300$ & 1.990948 & 4e-06 & 1.681748 & 3e-06 & 1.959229 & 4e-06 & 1.770892 & 3e-06\\
			\hline
			$\sigma_X = 10000, \sigma_Y = 1000$ & 5.329640 & 3e-05 & 1.773820 & 2e-06 & 1.887014 & 4e-06 & 2.648300 & 6e-06\\
			\hline
		\end{tabular}
	\end{footnotesize}
\end{table}
\begin{table}[H]

	\caption{$\rr$ Estimates and Std. Errs, SIRREPAR Model,
		Other Models, $X_0 = 99950, Y_0 = 50$, 
		$\sigma_X = 10, \sigma_Y = 1$}
	\begin{footnotesize}
		\hskip -1cm
		\begin{tabular}{l|r|r|r|r|r|r|r|r}
			\hline
			Data Set & Auto Est & Auto SE & AutoM Est & AutoM SE & Norm Est & Norm SE & NormM Est & NormM SE\\
			\hline
			0th & 3.272461 & 0e+00 & 3.275535 & 0e+00 & 3.135010 & 0e+00 & 3.235197 & 0e+00\\
			\hline
			1st & 1.038125 & 0e+00 & 1.037880 & 0e+00 & 1.037903 & 0e+00 & 1.037881 & 0e+00\\
			\hline
			2nd & 1.198760 & 1e-06 & 1.198526 & 1e-06 & 1.198864 & 1e-06 & 1.198616 & 1e-06\\
			\hline
			3rd & 1.202489 & 1e-06 & 1.202071 & 1e-06 & 1.202246 & 1e-06 & 1.202355 & 1e-06\\
			\hline
			4th & 1.210605 & 1e-06 & 1.210605 & 1e-06 & 1.210220 & 1e-06 & 1.210199 & 1e-06\\
			\hline
			Linear SIR & 1.274175 & 1e-06 & 1.273799 & 1e-06 & 1.274314 & 1e-06 & 1.274075 & 1e-06\\
			\hline
		\end{tabular}
	\end{footnotesize}
\end{table}

@@

	\caption{$\rr$ Estimates and Std. Errs, SIRLMA Model,
		Baseline Data, $X_0 = 99950, Y_0 = 50$, 
		$\sigma_X = 10, \sigma_Y = 1$}
	\begin{footnotesize}
		\hskip -1cm
		\begin{tabular}{l|r|r|r|r|r|r|r|r}
			\hline
			Data Set & Auto Est & Auto SE & AutoM Est & AutoM SE & Norm Est & Norm SE & NormM Est & NormM SE\\
			\hline
			Baseline 1 & 0.864913 & 0.203402 & 1.739858 & 0.122632 & 1.359771 & 0.919629 & 1.173245 & 0.096355\\
			\hline
			Baseline 2 & 1.485664 & 1.654031 & 1.294412 & 0.618155 & 1.461580 & 0.734907 & 1.186621 & 0.091633\\
			\hline
			Baseline 3 & 1.082572 & 0.088142 & 1.389817 & 0.117032 & 0.615994 & 1.496674 & 1.088364 & 0.089282\\
			\hline
			Baseline 4 & 1.088362 & 0.367110 & 1.370251 & 0.159221 & 2.683109 & 27.981877 & 1.090398 & 0.059515\\
			\hline
			Baseline 5 & 0.871650 & 0.100744 & 1.438190 & 0.382650 & 0.829591 & 0.120911 & 0.924238 & 0.188305\\
			\hline
		\end{tabular}
	\end{footnotesize}
\end{table}

@@

	\caption{$\rr$ Estimates and Std. Errs, SIRLMA Model,
		Different Starting Populations, 
		$\sigma_X = 10, \sigma_Y = 1$}
	\begin{footnotesize}
		\hskip -1.7cm
		\begin{tabular}{l|r|r|r|r|r|r|r|r}
			\hline
			Data Set & Auto Est & Auto SE & AutoM Est & AutoM SE & Norm Est & Norm SE & NormM Est & NormM SE\\
			\hline
			$X_0 = 99999, Y_0 = 1$ & 1.713333 & 1.757278 & 1.187769 & 0.515629 & 1.451833 & 59.746089 & 1.068633 & 1.809596\\
			\hline
			$X_0 = 99990, Y_0 = 10$ & 1.197457 & 0.192831 & 0.674259 & 0.090168 & 1.095143 & 0.143146 & 1.199437 & 0.106393\\
			\hline
			$X_0 = 99900, Y_0 = 100$ & 0.796760 & 0.488540 & 1.022290 & 0.070029 & 0.024273 & 4.564245 & 1.265712 & 0.080303\\
			\hline
			$X_0 = 99000, Y_0 = 1000$ & 1.431229 & 0.105605 & 2.091993 & 0.340798 & 2.183329 & 0.428090 & 1.812900 & 0.122106\\
			\hline
		\end{tabular}
	\end{footnotesize}
\end{table}

>>>>

We then generate random errors that are added to the X and Y compartments at each time step in order to simulate some form of randomness. \textbf{The sum of these was then subtracted from the Z compartment in order to keep the total population in the system constant.} We generated data sets with two different types of errors: Gaussian and autoregressive. \textbf{The Gaussian errors are independently distributed with mean 0 and constant variance for the entire length of the time series. The autoregressive errors are generated from a first-order process of the form: $$ \epsilon_{t} = \rho * \epsilon_{t-1} + \delta_{t}$$, where $\rho$ is fixed throughout and $\delta_{t} \sim N(0, \sigma)$ with constant $\sigma$.}

@@

%% What kind of graphs should we throw in?

%% SG: Forest plots!

@@

\begin{table}[H]
	\caption{$\rr$ Estimates and Std. Errs, SIR Model, 
		Baseline Data, $X_0 = 99950, Y_0 = 50$, 
		$\sigma_X = 10, \sigma_Y = 1$}
	\begin{footnotesize}
		\hskip -1cm
		\begin{tabular}{l|r|r|r|r|r|r|r|r}
			\hline
			Data Set & Auto Est & Auto SE & AutoM Est & AutoM SE & Norm Est & Norm SE & NormM Est & NormM SE\\
			\hline
			Baseline1 & 1.199737 & 0.000476 & 1.199557 & 0.000476 & 1.199737 & 0.000475 & 1.199737 & 0.000475\\
			\hline
			Baseline2 & 1.199737 & 0.000475 & 1.200380 & 0.000481 & 1.200376 & 0.000482 & 1.200376 & 0.000482\\
			\hline
			Baseline3 & 1.200615 & 0.000485 & 1.199557 & 0.000476 & 1.200380 & 0.000481 & 1.200298 & 0.000479\\
			\hline
			Baseline4 & 1.200376 & 0.000481 & 1.200061 & 0.000479 & 1.200380 & 0.000481 & 1.200602 & 0.000484\\
			\hline
			Baseline5 & 1.200376 & 0.000481 & 1.200376 & 0.000482 & 1.200298 & 0.000479 & 1.200602 & 0.000484\\
			\hline
		\end{tabular}
	\end{footnotesize}
\end{table}

@@

	\caption{$\rr$ Estimates and Std. Errs, SIR Model,
		Different Starting Populations, 
		$\sigma_X = 10, \sigma_Y = 1$}
	\begin{footnotesize}
		\hskip -1.7cm
		\begin{tabular}{l|r|r|r|r|r|r|r|r}
			\hline
			Data Set & Auto Est & Auto SE & AutoM Est & AutoM SE & Norm Est & Norm SE & NormM Est & NormM SE\\
			\hline
			$X_0 = 99999, Y_0 = 1$ & 1.214968 & 0.095795 & 1.236988 & 0.096579 & 1.218704 & 0.099065 & 1.218704 & 0.096508\\
			\hline
			$X_0 = 99990, Y_0 = 10$ & 1.219334 & 0.006658 & 1.219334 & 0.006854 & 1.219596 & 0.017843 & 1.219596 & 0.017847\\
			\hline
			$X_0 = 99900, Y_0 = 100$ & 1.199311 & 0.000166 & 1.200216 & 0.000170 & 1.200336 & 0.000170 & 1.200336 & 0.000170\\
			\hline
			$X_0 = 99000, Y_0 = 1000$ & 1.199807 & 0.000029 & 1.199807 & 0.000029 & 1.200160 & 0.000029 & 1.200160 & 0.000029\\
			\hline
		\end{tabular}
	\end{footnotesize}
\end{table}

@@

	\caption{$\rr$ Estimates and Std. Errs, SIR Model, 
		Different Variances, $X_0 = 99000$, $Y_0 = 1000$}
	\begin{footnotesize}
		\hskip -1.7cm
		\begin{tabular}{l|r|r|r|r|r|r|r|r}
			\hline
			Error & Auto Est & Auto SE & AutoM Est & AutoM SE & Norm Est & Norm SE & NormM Est & NormM SE\\
			\hline
			$\sigma_X = 10, \sigma_Y = 1$ & 1.200061 & 2.9e-05 & 1.200005 & 2.9e-05 & 1.199951 & 2.9e-05 & 1.199916 & 2.9e-05\\
			\hline
			$\sigma_X = 100, \sigma_Y = 10$ & 1.200317 & 2.9e-05 & 1.200427 & 2.9e-05 & 1.199963 & 2.9e-05 & 1.199734 & 2.9e-05\\
			\hline
			$\sigma_X = 500, \sigma_Y = 50$ & 1.201642 & 2.8e-05 & 1.201871 & 2.8e-05 & 1.199996 & 2.9e-05 & 1.198872 & 2.9e-05\\
			\hline
			$\sigma_X = 1000, \sigma_Y = 100$ & 1.203259 & 2.8e-05 & 1.203811 & 2.8e-05 & 1.199985 & 2.9e-05 & 1.197928 & 2.9e-05\\
			\hline
			$\sigma_X = 2000, \sigma_Y = 200$ & 1.206447 & 2.7e-05 & 1.207566 & 2.7e-05 & 1.199849 & 2.9e-05 & 1.195612 & 3.0e-05\\
			\hline
			$\sigma_X = 5000, \sigma_Y = 500$ & 1.215906 & 2.5e-05 & 1.218773 & 2.5e-05 & 1.199656 & 2.9e-05 & 1.189382 & 3.2e-05\\
			\hline
			$\sigma_X = 7500, \sigma_Y = 750$ & 1.223554 & 2.3e-05 & 1.228037 & 2.4e-05 & 1.199579 & 2.9e-05 & 1.183914 & 3.4e-05\\
			\hline
			$\sigma_X = 10000, \sigma_Y = 1000$ & 1.230992 & 2.2e-05 & 1.237142 & 2.2e-05 & 1.199381 & 2.9e-05 & 1.178701 & 3.6e-05\\
			\hline
			$\sigma_X = 15000, \sigma_Y = 1500$ & 1.245535 & 1.9e-05 & 1.255188 & 2.0e-05 & 1.199137 & 2.9e-05 & 1.168520 & 4.1e-05\\
			\hline
		\end{tabular}
	\end{footnotesize}
\end{table}

@@

	\caption{$\rr$ Estimates and Std. Errs, SIR Model,
		Other Models, $X_0 = 99950, Y_0 = 50$, 
		$\sigma_X = 10, \sigma_Y = 1$}
	\begin{footnotesize}
		\hskip -1cm
		\begin{tabular}{l|r|r|r|r|r|r|r|r}
			\hline
			Data Set & Auto Est & Auto SE & AutoM Est & AutoM SE & Norm Est & Norm SE & NormM Est & NormM SE\\
			\hline
			0th & 0.005468 & 0.000745 & -0.034869 & 0.000764 & -0.034869 & 7.4e-04 & 0.034869 & 0.000673\\
			\hline
			1st & 1.038004 & 0.000029 & 1.037900 & 0.000029 & 1.037826 & 2.9e-05 & 1.037826 & 0.000029\\
			\hline
			2nd & 1.199663 & 0.000045 & 1.198627 & 0.000045 & 1.199663 & 4.5e-05 & 1.198949 & 0.000045\\
			\hline
			3rd & 1.202909 & 0.000043 & 1.202282 & 0.000043 & 1.202414 & 4.3e-05 & 1.202414 & 0.000043\\
			\hline
			4th & 1.211092 & 0.000047 & 1.211092 & 0.000047 & 1.209479 & 4.7e-05 & 1.211092 & 0.000047\\
			\hline
			Linear SIR & 1.274529 & 0.000034 & 1.273768 & 0.000034 & 1.275057 & 3.4e-05 & 1.274745 & 0.000034\\
			\hline
		\end{tabular}
	\end{footnotesize}
\end{table}

@@

	\caption{$\rr$ Estimates and Std. Errs, SIRREPAR Model,
		Baseline Data, $X_0 = 99950, Y_0 = 50$, 
		$\sigma_X = 10, \sigma_Y = 1$}
	\begin{footnotesize}
		\hskip -1cm
		\begin{tabular}{l|r|r|r|r|r|r|r|r}
			\hline
			Data Set & Auto Est & Auto SE & AutoM Est & AutoM SE & Norm Est & Norm SE & NormM Est & NormM SE\\
			\hline
			Baseline 1 & 1.200196 & 1e-06 & 1.199942 & 1e-06 & 1.200108 & 1e-06 & 1.199965 & 1e-06\\
			\hline
			Baseline 2 & 1.199574 & 1e-06 & 1.199733 & 1e-06 & 1.199922 & 1e-06 & 1.200219 & 1e-06\\
			\hline
			Baseline 3 & 1.199909 & 1e-06 & 1.200416 & 1e-06 & 1.199851 & 1e-06 & 1.200009 & 1e-06\\
			\hline
			Baseline 4 & 1.199735 & 1e-06 & 1.199829 & 1e-06 & 1.199925 & 1e-06 & 1.199856 & 1e-06\\
			\hline
			Baseline 5 & 1.199849 & 1e-06 & 1.199683 & 1e-06 & 1.199943 & 1e-06 & 1.199900 & 1e-06\\
			\hline
		\end{tabular}
	\end{footnotesize}
\end{table}

@@

	\caption{$\rr$ Estimates and Std. Errs, SIRREPAR Model,
		Different Starting Populations, 
		$\sigma_X = 10, \sigma_Y = 1$}
	\begin{footnotesize}
		\hskip -1.7cm
		\begin{tabular}{l|r|r|r|r|r|r|r|r}
			\hline
			Data Set & Auto Est & Auto SE & AutoM Est & AutoM SE & Norm Est & Norm SE & NormM Est & NormM SE\\
			\hline
			$X_0 = 99999, Y_0 = 1$ & 1.209265 & 3.7e-05 & 1.198242 & 3.5e-05 & 1.193162 & 3.4e-05 & 1.200995 & 3.5e-05\\
			\hline
			$X_0 = 99990, Y_0 = 10$ & 1.202026 & 4.0e-06 & 1.198515 & 4.0e-06 & 1.199652 & 4.0e-06 & 1.199716 & 4.0e-06\\
			\hline
			$X_0 = 99900, Y_0 = 100$ & 1.199895 & 1.0e-06 & 1.199895 & 1.0e-06 & 1.199976 & 1.0e-06 & 1.200103 & 1.0e-06\\
			\hline
			$X_0 = 99000, Y_0 = 1000$ & 1.200089 & 0.0e+00 & 1.200008 & 0.0e+00 & 1.199992 & 0.0e+00 & 1.199985 & 0.0e+00\\
			\hline
		\end{tabular}
	\end{footnotesize}
\end{table}

@@

	\caption{$\rr$ Estimates and Std. Errs, SIRREPAR Model,
		Different Variances, 
		$X_0 = 99000, Y_0 = 1000$}
	\begin{footnotesize}
		\hskip -1.7cm
		\begin{tabular}{l|r|r|r|r|r|r|r|r}
			\hline
			Data Set & Auto Est & Auto SE & AutoM Est & AutoM SE & Norm Est & Norm SE & NormM Est & NormM SE\\
			\hline
			$\sigma_X = 10, \sigma_Y = 1$ & 1.199998 & 0 & 1.199990 & 0 & 1.200027 & 0 & 1.199972 & 0\\
			\hline
			$\sigma_X = 100, \sigma_Y = 10$ & 1.199920 & 0 & 1.199837 & 0 & 1.200179 & 0 & 1.199611 & 0\\
			\hline
			$\sigma_X = 500, \sigma_Y = 50$ & 1.199579 & 0 & 1.199154 & 0 & 1.200844 & 0 & 1.198063 & 0\\
			\hline
			$\sigma_X = 1000, \sigma_Y = 100$ & 1.199168 & 0 & 1.198307 & 0 & 1.201705 & 0 & 1.196130 & 0\\
			\hline
			$\sigma_X = 2000, \sigma_Y = 200$ & 1.198425 & 0 & 1.196618 & 0 & 1.203466 & 0 & 1.192321 & 0\\
			\hline
			$\sigma_X = 5000, \sigma_Y = 500$ & 1.196655 & 0 & 1.191769 & 0 & 1.208871 & 0 & 1.181229 & 0\\
			\hline
			$\sigma_X = 7500, \sigma_Y = 750$ & 1.195734 & 0 & 1.187972 & 0 & 1.213591 & 0 & 1.172358 & 0\\
			\hline
			$\sigma_X = 10000, \sigma_Y = 1000$ & 1.195439 & 0 & 1.184353 & 0 & 1.218455 & 0 & 1.163930 & 0\\
			\hline
			$\sigma_X = 15000, \sigma_Y = 1500$ & 1.196493 & 0 & 1.177762 & 0 & 1.228683 & 0 & 1.148505 & 0\\
			\hline
		\end{tabular}
	\end{footnotesize}
\end{table}
\begin{table}[H]

	\caption{$\rr$ Estimates and Std. Errs, SIRREPAR Model,
		Other Models, $X_0 = 99950, Y_0 = 50$, 
		$\sigma_X = 10, \sigma_Y = 1$}
	\begin{footnotesize}
		\hskip -1cm
		\begin{tabular}{l|r|r|r|r|r|r|r|r}
			\hline
			Data Set & Auto Est & Auto SE & AutoM Est & AutoM SE & Norm Est & Norm SE & NormM Est & NormM SE\\
			\hline
			0th & 2.803084 & 0e+00 & 2.663158 & 0e+00 & 2.688581 & 0e+00 & 2.756037 & 0e+00\\
			\hline
			1st & 1.038122 & 0e+00 & 1.037880 & 0e+00 & 1.037900 & 0e+00 & 1.037887 & 0e+00\\
			\hline
			2nd & 1.198739 & 1e-06 & 1.198544 & 1e-06 & 1.198847 & 1e-06 & 1.198585 & 1e-06\\
			\hline
			3rd & 1.202419 & 1e-06 & 1.202136 & 1e-06 & 1.202294 & 1e-06 & 1.202288 & 1e-06\\
			\hline
			4th & 1.210605 & 1e-06 & 1.210605 & 1e-06 & 1.210274 & 1e-06 & 1.210259 & 1e-06\\
			\hline
			Linear SIR & 1.274256 & 1e-06 & 1.273828 & 1e-06 & 1.274260 & 1e-06 & 1.274030 & 1e-06\\
			\hline
		\end{tabular}
	\end{footnotesize}
\end{table}

@@

	\caption{$\rr$ Estimates and Std. Errs, SIRLMA Model,
		Baseline Data, $X_0 = 99950, Y_0 = 50$, 
		$\sigma_X = 10, \sigma_Y = 1$}
	\begin{footnotesize}
		\hskip -1cm
		\begin{tabular}{l|r|r|r|r|r|r|r|r}
			\hline
			Data Set & Auto Est & Auto SE & AutoM Est & AutoM SE & Norm Est & Norm SE & NormM Est & NormM SE\\
			\hline
			Baseline 1 & 1.269690 & 0.120767 & 0.130935 & 10.750359 & 1.154610 & 0.065991 & 1.397649 & 0.233918\\
			\hline
			Baseline 2 & 1.187856 & 0.168327 & 1.121309 & 0.040461 & 1.193012 & 0.081712 & 1.357958 & 0.199538\\
			\hline
			Baseline 3 & 0.812981 & 0.084419 & 1.092512 & 0.034560 & 1.179720 & 0.054902 & 1.233221 & 0.060551\\
			\hline
			Baseline 4 & 1.180116 & 0.078889 & 1.168589 & 0.134484 & 1.293454 & 0.271027 & 1.165880 & 0.036177\\
			\hline
			Baseline 5 & 0.853203 & 0.064872 & 1.116949 & 0.041290 & 1.198555 & 0.106425 & 1.161485 & 0.032157\\
			\hline
		\end{tabular}
	\end{footnotesize}
\end{table}

@@

	\caption{$\rr$ Estimates and Std. Errs, SIRLMA Model,
		Different Starting Populations, 
		$\sigma_X = 10, \sigma_Y = 1$}
	\begin{footnotesize}
		\hskip -1.7cm
		\begin{tabular}{l|r|r|r|r|r|r|r|r}
			\hline
			Data Set & Auto Est & Auto SE & AutoM Est & AutoM SE & Norm Est & Norm SE & NormM Est & NormM SE\\
			\hline
			$X_0 = 99999, Y_0 = 1$ & 1.185172 & 1.285564 & 1.158778 & 0.152094 & 0.859907 & 83.111543 & 1.116840 & 0.064265\\
			\hline
			$X_0 = 99990, Y_0 = 10$ & 0.934239 & 3.360057 & 0.944893 & 0.034982 & 1.101154 & 0.287314 & 6.153800 & 1525.693988\\
			\hline
			$X_0 = 99900, Y_0 = 100$ & 1.255903 & 0.086428 & 0.462015 & 0.325984 & 1.250009 & 0.051102 & 1.193192 & 0.035157\\
			\hline
			$X_0 = 99000, Y_0 = 1000$ & 1.205152 & 0.005332 & 1.193656 & 0.005244 & 1.199742 & 0.004094 & 1.208671 & 0.004804\\
			\hline
		\end{tabular}
	\end{footnotesize}
\end{table}
